%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Palantir Technologies} % Organization
    {Palo Alto, California, USA} % Location
    {May. 2022 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a new implementation of an existing system to leverage provider-agnostic blob storage.}
        \item {Integrated two existing applications to allow for in-application documentation writing.}
       \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Teaching Assistant \& Undergraduate Software Lead, Fundamentals of Engineering for Honors} % Job title
    {Ohio State University College of Engineering} % Organization
    {Columbus, Ohio, USA} % Location
    {Aug. 2020 - Dec. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Taught a two-semester programming and engineering problem solving course for all first-year honors engineering students.}
        \item {Taught students technologies and skills such as Robotics, C, C++, MATLAB, Excel, and SOLIDWORKS.}
        \item {Led and contributed to many course software projects; developed in Typescript, Vue.js, Node.js, Python, C\# .NET, C and C++.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {IT Application Configuration Intern} % Job title
    {FirstEnergy} % Organization
    {Akron, Ohio, USA} % Location
    {May. 2021 - Aug. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Improved existing company database structure and integrated data from many sources into a cohesive Oracle database.}
        \item {Optimized and automated important company reports with VBA and Python, saving operators time daily.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Engineer Intern} % Job title
    {Patriot Software} % Organization
    {Canton, Ohio, USA} % Location
    {May. 2020 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed payroll and accounting web applications within a small, agile team, focusing on user onboarding and retention.}
        \item {Implemented OAuth 2.0 with Google into the existing authentication system.}
        \item {Created an internal dashboard reporting the effectiveness of a referral program.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
