%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Hightlighted Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {A Web Application for Fundamentals of Engineering for Honors Students and Instructors} % Description
    {Robot Store Website} % Project Name
    {} % Location
    {Spring 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Built a full-stack web application that enables students to purchase materials for their robot.}
        \item {Includes many instructor-facing pages and features to facilitate the ENGR 1282.01H course.}
        \item {Frontend: Node.js, TypeScript, and Express.js REST backend with a Vue.js and TypeScript SPA.}
        \item {Backend: Express.js and Typescript on Amazon EC2. Persistence: Amazon RDS, S3, and DynamoDB. Terraform for architecture.}
      \end{cvitems}
    }

%---------------------------------------------------------

    \cventry
    {A template for a Next.js app using Firebase's auth and Firestore database} % Description
    {Next.js, Firebase, and Typescript Template} % Project Name
    {\href{https://github.com/ahern55/next-firebase-typescript}{GitHub}} % Link
    {Summer 2022} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created an open-source app template leveraging many modern web technologies}
        \item {Framework: Next.js (React) | Authentication and Database: Firebase | Language: Typescript | Styles: Tailwind | Hosting and CD: Vercel}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {A Recipe Management Mobile App Availabke on the Apple App Store and Google Play.} % Description
    {Your Recipes} % Project Name
    {\href{https://github.com/ahern55/recipes}{GitHub}} % Link
    {Summer 2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Created a simple mobile app using Xamarin.Forms to allow users to easily store their recipes.}
        \item {Published the App to the leading App Stores, reaching hundreds of downloads}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
